target_offtarget

### 2025-04-14 manuscript_figures.Rmd
updating figure 1 to have dashed and solid lines
figure 1 update colors

@@

ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(Viral.load, mean_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load), linetype="dotted") +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 2,
              label = round(Coeff_x1, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 1.5*10000, 
                y = 2, 
                label = "Slope ="),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 6,
              label = round(R2, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 2*10000, 
                y = 6, 
                label = "R2 ="),
            size = 3.5) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
    xlab("Genome copies") + 
  ylab("Mean Read Depth") +
  scale_color_manual(values = cols) +
  guides(color = FALSE) +
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

persite_coverage_both |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(x = virus, y = percent_coverage, colour = Background)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_dodge(width = .75)) +
  facet_grid(~as.character(Viral.load), labeller = label_parsed) +
  theme_few() +
  ylab("Genome coverage") +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(values = cols2, labels = c("M1", "M2")) +
  scale_x_discrete(
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_y_continuous(limits = c(0, 1))

>>>>

lm_combined$virus_type =c('DNA','DNA','RNA','RNA','RNA','RNA')
```

@@

ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(Viral.load, mean_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load, linetype=virus_type, color = virus)) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 2,
              label = round(Coeff_x1, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 1.5*10000, 
                y = 2, 
                label = "Slope ="),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 6,
              label = round(R2, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 2*10000, 
                y = 6, 
                label = "R2 ="),
            size = 3.5) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
    xlab("Genome copies") + 
  ylab("Mean Read Depth") +
  scale_color_manual(values = cols) +
  guides(color = FALSE) +
  scale_linetype_manual(values=c("dotted", "solid"))+
  guides(linetype = FALSE)+
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

persite_coverage_both |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(x = virus, y = percent_coverage, colour = Background)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_dodge(width = .75)) +
  facet_grid(~as.character(Viral.load), labeller = label_parsed) +
  theme_few() +
  ylab("Genome coverage") +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 20, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(values = cols2, labels = c("M1", "M2")) +
  scale_x_discrete(
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_y_continuous(limits = c(0, 1))
